### 2023-12-23 tesis_Ashish/Chapter7/chapter7.tex
Updated 23Dec2023
update 24Dec2023

\begin{figure}[!htp]
  \centering
  \includegraphics[width=0.3 \columnwidth]{ashish_thesis/tepx_alllayer.png}
  \caption[TEPX double disk]{ \onehalfspacing R-Z view of the TEPX one double disk showing all four layers L1, L2, L3 and L4. Layer 1 and 3 has Ring 1, 2 and 3 modules, Layer 2 and 4 has Ring 2 and Ring 5 modules.}
  \label{fig:Innertracker_41}
\end{figure}

@@

\section{TEPX three fold coincidences}

@@

\begin{figure}[!htp]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/TEPX_threefold_linearity.png}
  \caption[Disk 4 Ring 2 three Fold Coincidences Linearity]{Left: Simulated mean number of three fold coincidences for all Disk 4 all rings as a function
    of pileup. Right: Deviation from linearity for Disk 4 all rings.}
  \label{fig:tepx_3foldcoin_allPU_3}
\end{figure}

>>>>

\begin{figure}[!htp]
  \centering
  \includegraphics[width=0.2 \columnwidth]{ashish_thesis/tepx_alllayer.png}
  \caption[TEPX double disk]{ \onehalfspacing R-Z view of the TEPX one double disk showing all four layers L1, L2, L3 and L4. Layer 1 and 3 has Ring 1, 3 and 5 modules, Layer 2 and 4 has Ring 2 and Ring 4 modules.}
  \label{fig:Innertracker_41}
\end{figure}

@@

\subsection{TEPX three fold coincidences}

@@

\begin{figure}[!htp]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/TEPX_threefold_linearity.png}
  \caption[Disk 4 all rings three Fold Coincidences Linearity]{Left: Simulated mean number of three fold coincidences for all Disk 4 all rings as a function
    of pileup. Right: Deviation from linearity for Disk 4 all rings.}
  \label{fig:tepx_3foldcoin_allPU_3}
\end{figure}
